\documentclass[12pt]{report}
% This is not mean to be a comprehensive coverage of tcolorbox. Rather, it is meant to provide a few boxes that you'll use on a practical basis. 

\usepackage{tcolorbox}
\tcbuselibrary{breakable}
\tcbuselibrary{skins}

\begin{document}

\section{simple boxes environments}
\begin{tcolorbox}
This is a box!
\end{tcolorbox}

%size can be (in desending size) normal, title, small, fbox, tight, minimal
\begin{tcolorbox}[size = title,drop shadow=black,title = "A  title"] 
This is a box!
\end{tcolorbox}

\begin{tcolorbox}[enhanced, drop fuzzy shadow]
This is a tcolorbox with a shadow! 
\end{tcolorbox}

%some more bells and whistles 
\begin{tcolorbox}[colback=red!5!white, colframe = red!50!blue, title = "A  title"]
This is a box!
    \begin{tcolorbox}[title = Nested Box]
    whoops I'm recursive!
    \end{tcolorbox}
\tcblower
This is lower! 
\end{tcolorbox}

%to set general settings 
\tcbset{colback=red!5!white, colframe = red!50!blue}
\begin{tcolorbox}
Now, we have the same style!
\end{tcolorbox}

\begin{tcolorbox}[reset]
I've reset my style but only for this box 
\end{tcolorbox}

\section{box inline commands}
Here, we use \verb|\tcbox| to do some interesting things 

This is a test \tcbox[on line]{hello World.} test done %images and tables can go in here too 

\section{Further customization}
You can make custom box environments 

%these are a few of the many options. "enhanced" is a required parameter 
\newtcolorbox{raisedbox}[2][]{colback=red!5!white,
colframe=red!75!black,fonttitle=\bfseries,
colbacktitle=red!85!black,enhanced,
attach boxed title to top center={yshift=-2mm},
title={#2},#1}

\begin{raisedbox}[colback=yellow]{Hello there} %you can always override a set parameter 
This is a box with special title defined as an environment. 
\end{raisedbox}

%these are a few of the many options. "enhanced" is a required parameter 
\newtcolorbox{standardbox}[2][]{colback=red!5!white,
colframe=red!75!black,fonttitle=\bfseries,
colbacktitle=red!85!black,
title={#2},#1}

\begin{standardbox}[]{Hello there} %you can always override a set parameter 
This is a standard box defined as an environment. 
\end{standardbox}

%for inline boxes (this one is good for highlighting)
\newtcbox{\mybox}[1][red]{on line,
arc=0pt,outer arc=0pt,colback=#1!10!white,colframe=#1!50!black,
boxsep=0pt,left=1pt,right=1pt,top=2pt,bottom=2pt,
boxrule=0pt,bottomrule=1pt,toprule=1pt}


This is a \mybox[blue]{test} and we believe in the power of \mybox[green]{boxes}. this can be quite helpful \mybox{especially when I need to highlight}


\end{document}